### 2017-10-13 Gruba/06-perf.tex

\stitle{Case Study for Feature Extraction}
In this section, we show the results of our demo system for user features extraction.
Considering the huge amount of users, we carefully selected one typical user for analysis.
Here we chose Mary(a famous drama and movie actor in China) as a representative.
The features extraction result for Mary is displayed in Fig.\ \ref{fig:userFeatures}.
Then we can see the basic information of Mary from the result. Her nickname is Actor Mary(演员马丽) and she is from Beijing(北京).
The number of followers of Mary is much more than the number of her friends.
The Sina Microblog tag she made for herself is "actor"(演员).
As the result of the long-term interest extraction shows, she is interested in stage performances(舞台表演), drama performances(话剧表演),films(电影光影) and so on, which is consistent with her actual situation.
What's more, the probability distribution of tweeting and retweeting behavior on different time periods in one day indicates that her activities at night is much more than daytime.
The time interval distribution of her behaviors is also shown in Fig.\ \ref{fig:userFeatures}. The time interval is mostly distributed within 48 hours, which indicates that she is a active user.
We developed a function for querying user's short-term interest.
Here we queried Mary's short-term interest between 09/01/2016 and 09/30/2016, and got it as shown in Fig.\ \ref{fig:userFeatures}. We analyzed her microblogs in the this period, she has been working tirelessly to promote the drama "Earl of Oolong Mountain"(乌龙山伯爵). So the results are in line with expectations.

\begin{figure}
  \centering
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure{
      \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure{
  \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure{
  \includegraphics[width=0.22\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
\end{figure}

>>>>

\stitle{Case Study for Feature Extraction}
In this section, we show the results of our demo system for user features extraction.
Considering the huge amount of users, we carefully selected one typical user for analysis.
Here we chose Mary(a famous drama and movie actress in China) as an example.
The feature extraction result for Mary is depicted in Fig.\ \ref{fig:userFeatures}.
Then we can see the basic information of Mary in Sub-Fig.\ \ref{fig:userFeatures:uf-1}: her nickname is Actress Mary (演员马丽) and she is from Beijing (北京).
Mary has more followers than followees.
The Sina Microblog tag she made for herself is ``actress'' (演员).
As to the long-term interest, she is interested with stage performance (舞台表演), drama (话剧表演),film (电影光影) and so on as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-2}, which is consistent with her tag.
The probability distribution of tweeting and retweeting indicates that she is more active at night than daytime as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-3} and \ref{fig:userFeatures:uf-4}.
According to Sub-Fig.\ \ref{fig:userFeatures:uf-5} and \ref{fig:userFeatures:uf-6}, the interval between her two tweeted/retweeted microblogs is mostly within 48 hours, showing she is an active user.
Mary's short-term interest, e.g. from 09/01/2016 to 09/30/2016, is shown in Sub-Fig.\ \ref{fig:userFeatures:uf-7}, which indicates she had been busy with promoting the drama ``Earl of Oolong Mountain'' (乌龙山伯爵). So the results are in line with expectations, as drama (话剧) and stage (舞台) in Sub-Fig.\ \ref{fig:userFeatures:uf-7}.

\begin{figure*}
  \centering
  \subfigure{
      \label{fig:userFeatures:uf-1}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-2}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-3}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-4}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-5}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-6}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-7}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure{
      \label{fig:userFeatures:uf-8}
      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
\end{figure*}
